Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-03 prop_letter.tex
section KS is a messgit add prop_letter.tex git add prop_letter.tex

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1]\ }
\newcommand{\rmd}{\mathrm{d}}

@@

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome
of a theory that is contextual depends upon
whether  compatible sets of observables are measured together or
separately; a non-contextual theory gives the same results in either
case.  A classic example of the varying opinions on the impact of
imprecision is the disagreement between
Meyer~\cite{PhysRevLett.83.3751} and 
Mermin~\cite{Mermin1999}  on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.  The Kochen-Specker  
theorem is in essence a
mathematical statement about contextuality, asserting that
in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator~$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
assign definite values $0$ or $1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration, leading him to assert that the
impact of Meyer's negative result is
``unsupportable''~\citep{Mermin1999}.  The debate on
whether contextuality is consistent with experimental
outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

@@

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the naïve addition of intervals would give
$\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
interval. Moreover the event $E\cup\overline{E}$ is the identity event
covering the entire space; its probability interval should be $[1,1]$
which is sharper than $[0.9,1.1]$. The problem is that the two
intervals are correlated: there is more information in the combined
event than in each event separately. In our example, even though the
``true'' probability of $E$ can be anywhere in the range $[0.2,0.3]$
and the ``true'' probability of~$\overline{E}$ can be in anywhere in
the range $[0.7,0.8]$, the values are not independent. Any value of
$\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq 0.75$. To account
for such subtleties, the axioms of interval-valued probability do not
use a strict equality for the combination of disjoint events. The
correct constraint regarding the probability of $E_1\cup E_2$ when
$E_1$ and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
combination with the requirement for the identity event would force
$\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.

@@

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM~$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator~$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projectors $P_0$
  and $P_1$ with $P_0P_1=P_1P_0$,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
classical IVPMs with quantum probability measures.

@@

The proof that QIVPMs become classical IVPMs when the space of events
includes only mutually commuting events is presented in detail in the
long version of this paper~\cite{HOSTunpublished}. The idea of the
proof is as follows. Given a subspace of commuting events $\events_C$,
we can construct a partial orthonormal basis by diagonalization and
complete it to a full orthonormal basis $\overline{\events_C}$. We
then build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis. This correspondence leads to a crucial
property in our setting.

@@

Our generalization of quantum probability measures to QIVPMs allows us
to strengthen the scope of one of the fundamental theorems of quantum
information: the Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}. Our finite-precision
extension of the theorem will suggest a resolution to the debate
initiated by Meyer and Mermin on the relevance of the Kochen-Specker
to experimental, and hence finite-precision, quantum
measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
Specifically, the original Kochen-Specker theorem is formulated under
the assumption that all observables of a quantum mechanical system
have \emph{definite values at all times}~\cite{Held2016}. Our
interval-valued probability framework will allow us to state, and
prove, a stronger version of the theorem that holds even if the
observables have values that are only definite up to some specific
parameter that quantifies experimental uncertainty. Put differently,
our stronger statement and theorem quantifies Mermin's
intuition~\citep{Mermin1999}:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case.
\end{quote}

@@

When $\delta=0$, every event must be assigned a probability in either
interval $[0,0]$ or $[1,1]$, i.e., every event is completely
determined with certainty. As $\delta$ gets larger, the QIVPM allows for
more indeterminate behavior. For example, when $\delta=\frac{1}{3}$,
two possible collections of intervals\nb$\mathscr{I}$ could be 
$\left\{ \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],
\necess\right\}$ and $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],
\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],
\left[\frac{5}{6},\frac{5}{6}\right],\necess\right\}$. Our technical result will be
that for ``small enough'' $\delta$, a variant of the Kochen-Specker
result is still valid. To state and prove this generalization we will first
reformulate the original Kochen-Specker theorem as a statement regarding the
non-existence of $0$-deterministic QIVPM. We will then strengthen this
result to show the non-existence of any $\delta$-deterministic QIVPM
when $\delta < 1/3$ and the Hilbert space dimension is greater than
2.

\amr{Fix below until next marker}

A 0-deterministic QIVPM\nb$\bar{\mu}$ has an important property
regarding to the expectation values of a family of $M$ commuting
observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative
to $\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
commutes, they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
Since $\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and
a unique quantum probability measure\nb$\mu$ exists such that $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
and $\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
$\mu\left(\proj{k}\right)=1$ if and only if $k=k_{0}$\nb\citep{HOSTunpublished}.
If we denote the product observables\nb$\prod_{j=1}^{M}\mathbf{O}_{j}$
as $\overline{\mathbf{O}}$, the expectation values of the observables\nb$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
and $\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both $\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$
and $\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product
of the eigenvalues corresponding to the pure state\nb$\ket{k_{0}}$
for each observable\nb$\mathbf{O}_{j}$. By adopting an intuitive
product rule\nb$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $,
we have the following property: 
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}

\amr{End marker}

We now state and prove a theorem that is equivalent in scope to the
original Kochen-Specker theorem but that is formulated in terms of
$0$-deterministic QIVPMs.

\begin{thm} [0-Deterministic Variant of
  Kochen-Specker] \label{thm:Kochen-Specker} Given a Hilbert space
  $\Hilb$ of dimension~$d\ge3$, there is no 0-deterministic
  measure~$\bar{\mu}$ mapping every event to either $[0,0]$ or $[1,1]$.
\end{thm}

To explain why this result is equivalent to the original
Kochen-Specker theorem and to prove it at the same time, we proceed by
assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive a
contradiction to the original Kochen-Specker theorem using the same
nine observables $\mathbf{O}_{ij}$ used in the ``Mermin-Peres'' proof
of the Kochen-Specker
theorem~\cite{Mermin1990Simple,peres1995quantum}:
{\renewcommand{\arraystretch}{2}%
\begin{center}
\begin{tabular}{|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}\,,
\par\end{center}
}
\noindent where
$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are Pauli
matrices acting on a pair of spin-$\frac{1}{2}$ states.  The
observables in the Mermin-Peres square must have expectation
values~$\left\{ 1\right\} $ or $\left\{ -1\right\} $.  In each row and
column, the operators commute, and each operator is the product of two
others, except in the third column, where
$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clearly impossible to find a QIVPM~$\bar{\mu}$ such
that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$ satisfies
Eq.~(\ref{eq:Kochen-Specker-Rules}).

@@

We call a state $\rho$ a \emph{totally mixed state} if
$0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $. We also
define a notion of distance based on the following norm of a
matrix~$A$ as
$\left\Vert A\right\Vert
=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}. Now
consider the following collection of intervals:
\begin{eqnarray}
\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
 &  & \cup\left\{ \left[0,0\right],\left[1,1\right]\right\} 
\end{eqnarray}
which are overlapping intervals with length~$1/n$ except the intervals
at each end.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\rmd}{\mathrm{d}}

@@

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome
of a theory that is contextual depends upon
whether  compatible sets of observables are measured together or
separately; a non-contextual theory gives the same results in either
case.  A classic example of the varying opinions on the impact of
imprecision is the disagreement between
Meyer~\cite{PhysRevLett.83.3751} and 
Mermin~\cite{Mermin1999}  on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.  The Kochen-Specker  
theorem is in essence a
mathematical statement about contextuality, asserting that
in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator~$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
assign definite values $0$ or~$1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration, leading him to assert that the
impact of Meyer's negative result is
``unsupportable''~\citep{Mermin1999}.  The debate on
whether contextuality is consistent with experimental
outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

@@

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the naïve addition of intervals would give
$\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
interval. Moreover the event $E\cup\overline{E}$ is the identity event
covering the entire space; its probability interval should be
$\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
two intervals are correlated: there is more information in the
combined event than in each event separately. In our example, even
though the ``true'' probability of $E$ can be anywhere in the range
$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be in
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint regarding the probability of
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
combination with the requirement for the identity event would force
$\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the
particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.

@@

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including $\imposs$
  and $\necess$ with addition and scalar multiplication defined as
  follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM~$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator~$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\imposs\,,\\
   &  & \bar{\mu}(\mathbb{1})=\necess\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)= \necess -\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projectors~$P_0$
  and~$P_1$ with $P_0P_1=P_1P_0$,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of the convexity condition of
Eq.~(\ref{eq:classicalconvex}). Thus our definition of QIVPMs merges
classical IVPMs with quantum probability measures.

@@

The proof that QIVPMs become classical IVPMs when the space of events
includes only mutually commuting events is presented in detail in the
long version of this paper~\cite{HOSTunpublished}. The idea of the
proof is as follows. Given a subspace of commuting events~$\events_C$,
we can construct a partial orthonormal basis by diagonalization and
complete it to a full orthonormal basis $\overline{\events_C}$. We
then build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis. This correspondence leads to a crucial
property in our setting.

@@

Our generalization of quantum probability measures to QIVPMs allows us
to strengthen the scope of one of the fundamental theorems of quantum
information: the Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}. Our
finite-precision extension of the theorem will suggest a resolution to
the debate initiated by Meyer and Mermin on the relevance of the
Kochen-Specker to experimental, and hence finite-precision, quantum
measurements~\citep{PhysRevLett.83.3751,Mermin1999,Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
Specifically, the original Kochen-Specker theorem is formulated under
the assumption that all observables of a quantum mechanical system
have \emph{definite values at all times}~\cite{Held2016}, i.e., they
have infinitely precise values at all times. Our interval-valued
probability framework will allow us to state, and prove, a stronger
version of the theorem that holds even if the observables have values
that are only definite up to some precision specified by a parameter
$\delta$. Put differently, our stronger statement and theorem
quantifies Mermin's intuition~\citep{Mermin1999}:
\begin{quote}
  \ldots although the outcomes deduced from such imperfect
  measurements will occasionally differ dramatically from those
  allowed in the ideal case, if the misalignment is very slight, the
  statistical distribution of outcomes will differ only slightly from
  the ideal case.
\end{quote}

@@

\noindent The definition puts no restrictions on the choice of
intervals, only on the assignment of intervals to events. When
$\delta=0$, every event must be assigned a probability in either
interval $\imposs$ or $\necess$, i.e., every event is completely
determined with certainty. As $\delta$ gets larger, the QIVPM allows
for more indeterminate behavior. % For example, when
% $\delta=\frac{1}{3}$, two possible collections of
% intervals\nb$\mathscr{I}$ could be
% $\left\{
%   \imposs,\left[0,\frac{1}{3}\right],\left[\frac{2}{3},1\right],
%   \necess\right\}$ and
% $\left\{ \imposs,\left[\frac{1}{6},\frac{1}{6}\right],
%   \left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],
%   \left[\frac{5}{6},\frac{5}{6}\right],\necess\right\}$.
Our technical result will be that for ``small enough'' $\delta$, a
variant of the Kochen-Specker result is still valid. To state and
prove this generalization we will first reformulate the original
Kochen-Specker theorem as a statement regarding the non-existence of
$0$-deterministic QIVPM. We will then strengthen this result to show
the non-existence of any $\delta$-deterministic QIVPM when
$\delta < 1/3$ and the Hilbert space dimension is greater than 2.

\begin{thm} [0-Deterministic Variant of
  Kochen-Specker] \label{thm:Kochen-Specker} Given a Hilbert space
  $\Hilb$ of dimension~$d\ge3$, there is no 0-deterministic
  measure~$\bar{\mu}$ mapping every event to either $\imposs$ or
  $\necess$.
\end{thm}

To explain why this result is equivalent to the original
Kochen-Specker theorem and to prove it at the same time, we proceed by
assuming a 0-deterministic QIVPM $\bar{\mu}$ and derive a
contradiction to the original Kochen-Specker theorem using the same
nine observables $\mathbf{O}_{ij}$ with both $i$ and $j$ in the range
${1,2,3}$ used in the ``Mermin-Peres'' proof of the Kochen-Specker
theorem~\cite{Mermin1990Simple,peres1995quantum}. These nine
observables are given below: {\renewcommand{\arraystretch}{2}%
\begin{center}
\begin{tabular}{|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}\,,
\par\end{center}
}
\noindent where
$\left\{\mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\}$ are the
Pauli matrices acting on a pair of spin-$\frac{1}{2}$ states. These
matrices satisfy
$\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Furthermore we have that the observables in the square satisfy the
following properties: each observable has expectation value~$1$
or~$-1$; in each row and column, the observables commute; and in each
row and column except the third column, each operator is the product
of the other two. To find a QIVPM~$\bar{\mu}$ \ldots

Therefore, it is clearly impossible to find a QIVPM~$\bar{\mu}$ such
that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$ satisfies
Eq.~(\ref{eq:Kochen-Specker-Rules}).

A 0-deterministic QIVPM~$\bar{\mu}$ has an important property
regarding to the expectation values of a family of $M$ commuting
observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$ relative to
$\bar{\mu}$. Since $\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$
commutes, they can be diagonalized by a common orthonormal
basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.  Since
$\bar{\mu}$ is 0-deterministic, a unique $\ket{k_{0}}$ and a unique
quantum probability measure~$\mu$ exists such that
$\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $ and
$\mu\left(P\right)\in\left\{ 0,1\right\} $ for all $P\in\events$;
$\mu\left(\proj{k}\right)=1$ if and only if
$k=k_{0}$~\citep{HOSTunpublished}.  If we denote the product
observables~$\prod_{j=1}^{M}\mathbf{O}_{j}$ as
$\overline{\mathbf{O}}$, the expectation values of the
observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$ and
$\expval{\overline{\mathbf{O}}}_{\bar{\mu}}$ are equal to the
singleton sets whose only elements are $\expval{\mathbf{O}_{j}}_{\mu}$
and $\expval{\overline{\mathbf{O}}}_{\mu}$, respectively. Both
$\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\mu}$ and
$\expval{\overline{\mathbf{O}}}_{\mu}$ are equal to the product of the
eigenvalues corresponding to the pure state~$\ket{k_{0}}$ for each
observable~$\mathbf{O}_{j}$. By adopting an intuitive product
rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{
  x_{0}x_{1}\right\} $, we have the following property:
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}

@@

We call a state $\rho$ a \emph{totally mixed state} if
$0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $. We also
define a notion of distance based on the following norm of a
matrix~$A$ as
$\left\Vert A\right\Vert
=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}. Now
consider the following collection of intervals:
\begin{eqnarray}
\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
 &  & \cup\{ \imposs, \necess \}
\end{eqnarray}
which are overlapping intervals with length~$1/n$ except the intervals
at each end.
